Changes in Patterns of Geometric Sign Groupings as a Model of Social Dynamics Across Aurignacian Phases

### 2025-05-27 paper/paper.qmd
render to docx

ggsave(maps_bar_plots, 
      filename =  "map-and_hist-plot.png",
       h = 10, w = 10,
       bg = "white")

knitr::include_graphics("map-and_hist-plot.png")

>>>>

ggsave(maps_bar_plots, 
      filename =  here::here("figures/map-and-hist-plot.png"),
       h = 10, w = 10,
       bg = "white")

knitr::include_graphics(here::here("figures/map-and-hist-plot.png"))
